Illusory Finger Stretching and Somatosensory Responses

### 2025-03-17 manuscript.qmd
Updated dockerfile and always activate reticulate

# create python environment and install packages
  if (processdata==1){
  install_miniconda()
  use_miniconda('r-reticulate')
  # install_python(version="3.10")
  py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
  }

>>>>

# create python environment and install packages
  # if (processdata==1){
  install_miniconda()
  use_miniconda('r-reticulate')
  # install_python(version="3.10")
  py_install(c('mne', 'numpy', 'scikit-learn', 'matplotlib', 'pandas', 'openpyxl'))
  # }
